miniKanren with fair search strategies

### 2019-05-20 Paper/paper.tex
more typesetting improv.

\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}1 {/fair}{{$_{fair}$}}3
  		   {→}{{$\rightarrow$}}1
  		   {×}{{$\times$}}1
  		   {conde}{{cond$^e$}}4
  		   {repeato}{{repeat$^o$}}6
}
%% scheme-list .

>>>>

\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
  		   {→}{{$\rightarrow$}}{1}
  		   {×}{{$\times$}}{1}
  		   {==}{{$\equiv$}}{1}
  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
  		   {repeato}{{repeat$^o$}}{6}
}
%% scheme-list .
